Capturing the geometric structure of our experiences and how we remember them

### 2018-07-25 main.tex
finished brain results

The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}. This makes it challenging to use the recall model directly to examine neural activity patterns during video viewing.  To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW ref).  We used the resulting path warp each voxel's timeseries as well as the recall model timeseries.  Then using a searchlight procedure (5mm), we computed the timepoint-by-timepoint correlation matrix over searchlight voxels. We vectorized the recall correlation and searchlight correlation.

>>>>

The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}. To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW ref).  We used the resulting alignment path to warp the fMRI timeseries (for each voxel) as well as the recall model timeseries.  Then using a searchlight procedure (5mm), we computed the timepoint-by-timepoint neural correlation matrix within each searchlight. To measure the similarity between the neural and behavioral correlation matrices, we vectorized and then correlated them. The result was a correlation value for each voxel representing the extent to which the brain data mirrored the recall data.  Finally, to test the significance of the correlation values, we phase shifted the recall models (100 permuations) and recomputed the correlation values. Significance was determined by ``real'' correlation values that exceeded the 95th percentile of this null distribution. The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants'' recalls.
